\providecommand{\main}{..}
\documentclass[../main.tex]{subfiles}
\usepackage{amsmath}

\title{Tinkham Electrodynamic response}
\author{\begin{telugu}హృదయ్ దీపక్ మల్లుభొట్ల\end{telugu}}
% want empty date
\predate{}
\date{}
\postdate{}

\begin{document}

	% !TeX spellcheck = en_GB
	\onlyinsubfile{\maketitle}
	\section{Tinkham's Superconductor response} \label{sec:TinkhamResponse}

	We'll talk about Tinkham's derivation\supercite{Tinkham}, which shows the same $\sigma\sim\frac{1}{q}$ dependence that's caused us issues.

	\subsection{Two-Fluid Model Drude Analysis} \label{subsec:twofluid}

	Summarising Drude here, for any particular channel parameterised by some scattering time $\tau_i$, where $i$ indexes the channel,\todo{Tinkham has a plus sign in the denominator of~\eqref{eq:tinkhamdrude}, and I have no idea why, or if it's related to other sign or complex conjugation differences}
	\begin{align}
		\sigma_i(\omega) &\equiv \sigma_{1i} - i \sigma_{2i} \\
		\sigma_i(\omega) &= \frac{\flatfrac{n_i e^2 \tau_i}{m}}{1 + i \omega \tau_i} \label{eq:tinkhamdrude}
	\end{align}
	For some two-fluid model, we can allow two channels $i \in \{n, s\}$, and describe the superconducting channel by sending $\tau_s \rightarrow \infty$.
	As Tinkham describes, this leads to a delta function, and we get for the total conductivity
	\begin{align}
		\sigma_1(\omega) &= \frac{\pi n_s e^2}{2m} \delta(\omega) + \frac{n_n e^2 \tau_n}{m} \\
		\sigma_2(\omega) &= \frac{n_s e^2}{m \omega}.
	\end{align}
	This by itself doesn't mean a ton, as this two-fluid model isn't expected to be a spectacular approximation.
	It does, however, point to a couple features we should expect for the superconductivity, which is that there still is dissipative flow for any non-zero frequency (where dissipative flow is controlled by $\sigma_1$).
	Also, we expect some specific signs for the conductivity's real and imaginary parts, and thus specific signs for the dielectric constant.
	With $\epsilon \sim i \sigma$, we should expect that $\epsilon$ has a positive real and imaginary part, if $\sigma_1$ and $\sigma_2$ are both positive.
	We don't end up seeing this in other forms, so we should investigate this.\todo{make sure the signs are consistent.}

	\subsection{BCS Electrodynamics} \label{subsec:bcscalc}

	We'll summarise here Tinkham's section 3.10, which calculates the electrodynamic response using the BCS theory.
	Our goal here is to try to summarise the specific list of assumptions that lead to the dissipative conductivity for arbitrary large wavevector.

	We begin by assuming that we have some perturbation to the Hamiltonian of the form
	\begin{equation}
		% Tinkham uses \mathscr rather than \mathcal, but that causes issues with luaotfload and rsfs apparently.
		\mathcal{H}_1 = \frac{ie\hbar}{2 m c} \sum_i \left( \nabla_i \cdot \vec{A} + \vec{A} \cdot \nabla_i \right)
	\end{equation}
	Then, as Tinkham describes, we can expand the wavevector in Fourier components: \todo{Why does Tinkham use $k$ in the sum?}
	\begin{equation}
		\vec{A}(\vec{r}) = \sum_{\vec{q}} \vec{a}(\vec{q}) e^{i \vec{q} \cdot \vec{r}}.
	\end{equation}
	This lets us write $\mathcal{H}_1$ as
	\begin{equation}
		\mathcal{H}_1 = - \frac{e \hbar}{m c}\sum_{\vec{k}, \vec{q}} \vec{k} \cdot \vec{a}(\vec{q}) c^\ast_{\vec{k} + \vec{q}, \sigma} c_{\vec{k}, \sigma}
	\end{equation}
	We now have to relate this using Chambers' form for the current transform thing\todo{Continue on with 3.10 notes}.

\end{document}
